\begin{itemize}
	\item \textbf{Scale Unit}: The name of the device directly used to gather data on weight.
	\item \textbf{Central Unit}:The name give to the unit where all the information is brought together, analysed and provided to the user of the system.
	\item \textbf{ADC}: Analogue To Digital Converter
	\item \textbf{Wheatstone Bridge}: A circuit configuration used to analyse components with changing resistance.
	\item \textbf{Instrumentation Amplifier}: A device that amplifies the difference between two voltages. 
	\item \textbf{ZigBee}: ZigBee is protocol for the digital radio communication.
	\item \textbf{Strain Gauges}:An electronic device that changes its resistive qualities based on the strain exerted on it.
	\item \textbf{raspberry Pi}:Raspberry Pi is a single-board computer, running a linux operating system.
	\item \textbf{Microcontroller}:Microcontroller is a small computer on a single integrated circuit containing a processor core, memory, and programmable input/output peripherals.
	\item \textbf{PCB}: Printed Circuit Board
	\item \textbf{PDIP}: Plastic Dual In-line Packages
	\item \textbf{TO-XX}: Isolated Plastick Package
	\item \textbf{GPIO}:General Purpose Input/Output
	\item \textbf{RF Transceiver}: it is a device which is doing both transmitting and recieving in the radio frequency range.
	\item \textbf{UART}: Universal Asynchronous Receiver/Transmitter
	\item \textbf{SDIP}: Shrink Dual Inline Package
	\item \textbf{STM32Fx}: Microcontroller that we are using for scale units.
	\item \textbf{Potentiometer}:Potentiometer is a three-terminal resistor with a sliding contact that forms an adjustable voltage divider.
	\item \textbf{Voltage Regulator}: A voltage regulator is designed to maintain a constant voltage level automatically
	\item \textbf{Molex Header}: Header used to interface with the PCBs.
	\item \textbf{HTTP}: Hypertext Transfer Protocol
	\item \textbf{TCP}: Transmission Control Protocol
\end{itemize}
